### 2022-08-05 README.Rmd
update readme

This repository contains the R code and other materials for the paper "Comparing corrosion control treatments for drinking water using a robust Bayesian generalized additive model", currently available as a [preprint](http://doi.org/10.26434/chemrxiv-2022-b3f72-v3). Bespoke functions used to fit the models are available as a separate package, [`bgamcar1`](https://github.com/bentrueman/bgamcar1).

>>>>

This repository contains the R code and other materials for the paper "Comparing corrosion control treatments for drinking water using a robust Bayesian generalized additive model", currently available as a [preprint](http://doi.org/10.26434/chemrxiv-2022-b3f72-v4). Bespoke functions used to fit the models are available as a separate package, [`bgamcar1`](https://github.com/bentrueman/bgamcar1).
